SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-14 paper/encoding.tex
added table fix and G out

\begin{enumerate}[label=\Alph*]
\item Every present molecule is considered to be active.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
\item Activity of molecules on the edges is driven by pairing inhibition.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
\item Version F with additional constraint that every edge is distinct.\ashu{encode this??}
%\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition with every edge is distinct.
%\item Activity of molecules on the nodes is based on Boolean function of presence of other moleculess and on edge by pairing inhibition with self-edges are allowed.
%\item Version F but self-edges are allowed.
\end{enumerate}
%
The version (A) is most basic where every present molecule is active.
%
In versions (B-D,F-H),
most general restriction is activity of the molecule is dependent on
the other molecules presence on the node.
%
In the versions (E-H), activity of the molecules on the edges
is dictated by pairing matrix; we call this process ``pairing
inhibition".
%
In the column 2-3 of table~\ref{table1}, we list the constraints involved
in each version.

>>>>

\begin{enumerate}[label=\Alph*]
\item Every present molecule is considered to be active.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
\item Activity of molecules on the edges is driven by pairing inhibition.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
%\item Version F with additional constraint that every edge is distinct.\ashu{encode this??}
%\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition with every edge is distinct.
%\item Activity of molecules on the nodes is based on Boolean function of presence of other moleculess and on edge by pairing inhibition with self-edges are allowed.
%\item Version F but self-edges are allowed.
\end{enumerate}
%
The version (A) is most basic where every present molecule is active.
%
In versions (B-D,F),
most general restriction is activity of the molecule is dependent on
the other molecules presence on the node.
%
In the versions (E,F), activity of the molecules on the edges
is dictated by pairing matrix; we call this process ``pairing
inhibition".
%
In the column 2-3 of table~\ref{table1}, we list the constraints involved
in each version.

### 2017-07-14 paper/experiments.tex
added table fix and G out

\begin{table}[t]
\centering
% \def\arraystretch{1.6}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    {\multirow{2}{*}{\textbf{Version}}}  & 
    \multicolumn{2}{c|}{\multirow{2}{*}{\textbf{Constraints}}} & 
    \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
   \cline{4-5}
   &  &  & \textbf{\textbf{Least connected}} & \textbf{Sampling: Guarantee}\\ \hline

A. & \multirow{5}{*}{
     \makecell{ \ref{eq:f0}--\ref{eq:fuse2},\\
     \ref{eq:reach1},\ref{eq:reach2},\\
     \ref{eq:drop1}--\ref{eq:drop4}}
     } 
& \ref{eq:ann},\ref{eq:aen} & No graph & No graph \\ \cline{3-5}
B. & & \ref{eq:anb},\ref{eq:aen} & No graph & No graph \\ \cline{3-5}
C. & & \ref{eq:ann},\ref{eq:aeb} & 3-connected & 3-connected \\  \cline{3-5}
D. & & \ref{eq:ann},\ref{eq:aep} & No graph & No graph \\ \cline{3-5}
E. & & \ref{eq:anb},\ref{eq:aeb} & 2-connected & 3-connected \\ \cline{3-5}
F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected & 4-connected \\ \cline{3-5}
G. & & \ref{eq:anb},\ref{eq:aeb},\ref{eq:ced} & 3-connected & 3-connected \\ \hline

>>>>

\begin{table}[t]
\centering
% \def\arraystretch{1.6}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    {\multirow{2}{*}{\textbf{Version}}}  & 
    \multicolumn{2}{c|}{\textbf{Constraints}} & 
    \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
   \cline{2-5}
   &  \textbf{Rest} & \textbf{Activity} & \textbf{\textbf{Least connected}} & \textbf{Sampling: Guarantee}\\ \hline

A. & \multirow{5}{*}{
     \makecell{ \ref{eq:f0}--\ref{eq:fuse2},\\
     \ref{eq:reach1},\ref{eq:reach2},\\
     \ref{eq:drop1}--\ref{eq:drop4}}
     } 
& \ref{eq:ann},\ref{eq:aen} & No graph & No graph \\ \cline{3-5}
B. & & \ref{eq:anb},\ref{eq:aen} & No graph & No graph \\ \cline{3-5}
C. & & \ref{eq:ann},\ref{eq:aeb} & 3-connected & 3-connected \\  \cline{3-5}
D. & & \ref{eq:ann},\ref{eq:aep} & No graph & No graph \\ \cline{3-5}
E. & & \ref{eq:anb},\ref{eq:aeb} & 2-connected & 3-connected \\ \cline{3-5}
F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected & 4-connected \\ \hline
%G. & & \ref{eq:anb},\ref{eq:aeb},\ref{eq:ced} & 3-connected & 3-connected \\ \hline
